On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
chaz

Before moving on to our proofs, we discuss briefly the computability and tightness of our results. [* DO THIS *]
%\pagebreak

@@

We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} requires only a polynomial number of samples distributed over a polynomial number of supports.}

>>>>

Before moving on to our proofs, we discuss briefly the computability and tightness of our results. [* DO THIS *]

We remark that if $k$ is held fixed, or if the size of the support set of reconstructing codes is known to be polynomial in $\bar m$ and $k$, then a practical (polynomial) amount of data is enough to determine the model.\footnote{In the latter case, a re-examination of the pigeonholing argument in the proof of Thm.~\ref{DeterministicUniquenessTheorem} shows that only a polynomial number of samples distributed over a polynomial number of supports.}
%\pagebreak

@@
